Deciding to Disclose

### 2015-06-18 Conclusion.tex
Trimming length

From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a relatively trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model to a degree. This is an important consideration, given that part of the argument in favour of a decision theoretic approach to agent building lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

@@

In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

>>>>

From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant. The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable. By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.  Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.

@@

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general. This also highlights an advantage of the \ac{BACCO} approach, in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

### 2015-06-18 Introduction.tex
Trimming length

The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g. \citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players. The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example. Alcohol consumption in the antenatal period is a significant issue in itself, and has been associated with many potentially negative consequences. For example, \citet{Andersen2012} report results from a large scale Danish cohort study suggesting that even low levels of consumption in early pregnancy increase the risk of spontaneous abortion, although \citet{Savitz2012} has suggested this may be attributable to a previously known link to absence of mornining sickness. Risk continues to the point of birth - \citet{Kesmodel2002} found a heightened risk to the infant - into childhood, with a metastudy by \citet{Latino-Martel2010} finding evidence on an increased risk of childhood \ac{AML}. Harm may also extend even further, and a review by \citet{Huizink2006} concluded that maternal alcohol consumption could be a contributing factor to \ac{ADHD}, and other learning impairments, but note methodological issues in a number of the papers. There is not, however, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day. In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.

@@

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem. In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, a single decision rule represents a pleasingly parsimonious alternative to numerous case specific production rules.

>>>>

The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g. \cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players. The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example. Alcohol consumption in the antenatal period is a significant issue in itself, although there is not, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day. In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.

@@

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem. In addition, rules are agnostic as to where the source of information, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, a single decision rule represents a parsimonious alternative to numerous case specific production rules.

### 2015-06-18 Methods.tex
Trimming length

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

@@

Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Sixteen emulators were built, covering each of the four outputs on all four decision models. These emulators were used to conduct a probabilistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

>>>>

Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.  Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

@@

Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and \ac{IQR} of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.

### 2015-06-18 Results.tex
Trimming length

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

\begin{figure}[H]
\includegraphics[width=119mm]{figures/ref_plot}
\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:referrals}}
\end{figure}

@@

Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/ref_sharing}
\end{adjustbox}
\caption{Impact of social learning on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:ref_sharing}
\end{figure}

@@

Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. This suggests, perhaps unsurprisingly, that what information is shared is significant to outcomes.

>>>>

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results, which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

@@

@@

Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions. Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.

@@

@@

Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:sharing_results}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. This suggests, perhaps unsurprisingly, that what information is shared is significant to outcomes.

### 2015-06-18 abstract_short.tex
Trimming length

In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.

>>>>

In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.
